---
title: "Largent_HW6_Part2"
output: html_document
---

Nice work! Try to give your functions more descriptive names. You can use comments
to let me know which problem you are solving.

```{r}
require(ggplot2)
require(grid)
```

1) This function, problem1, takes a data.frame and returns a data.frame. The new data.frame contains only columns that are composed of "integer" or "numeric" type variables. 

```{r}
problem1 <- function(indf){
  count <- 1;
  outdf = indf[1]
  for (i in 1:length(indf)) {
    if (any(class(indf[[i]]) == "numeric" | class(indf[[i]]) == "integer")) {
      outdf[count] <- indf[i]
      count <- count + 1
    }
  }
  if (count == 1) {
    outdf <- data.frame()
  }
return(outdf)
}
```

2) This function, problem2, takes a data.frame and returns a data.frame. The first part is the same as the code used in problem 1. The second part identifies all the combinations of variables - these are listed in column 1 - and the Pearson correlation between the variables - these are listed in column 2. No 

```{r}
problem2 <- function(indf){
  count <- 1;
  outdf = indf[1]
  for (i in 1:length(indf)) {
    if (any(class(indf[[i]]) == "numeric" | class(indf[[i]]) == "integer")) {
      outdf[count] <- indf[i]
      count <- count + 1
    }
  }
  if (count == 1) {
    outdf <- data.frame()
  }

  # Create all possible combinations of vectors in outdf 
  tempV = c();
  for(i in 1:(length(outdf)-1)) {
    for(j in (i+1):length(outdf)) {
      temp1 <- paste(colnames(outdf[i]),colnames(outdf[j]),sep="-")
      temp2 <- cor(outdf[i],outdf[j], method="pearson")
      tempV = rbind(tempV,c(temp1,temp2))
    }
  }
  outdf <- data.frame(tempV)
  colnames(outdf) <- c("Variables","Pearson_Corr")
return(outdf)
}
```

3) Finally, the last problem. This function, problem3, takes a data.frame and then creates scatterplots of all possible combinations of the numeric data included in the given data.frame. This code leverages the code used in problems 1 and 2. The scatterplots have a title that gives the names of the two variables and the corresponding Pearson coefficient. 

```{r}
problem3 <- function(indf){
  count <- 1;
  outdf = indf[1]
  for (i in 1:length(indf)) {
    if (any(class(indf[[i]]) == "numeric" | class(indf[[i]]) == "integer")) {
      outdf[count] <- indf[i]
      count <- count + 1
    }
  }
  if (count == 1) {
    outdf <- data.frame()
  }

  # Create all possible combinations of vectors in outdf 
  tempV = c();
  for(i in 1:(length(outdf)-1)) {
    for(j in (i+1):length(outdf)) {
      temp1 <- paste(colnames(outdf[i]),colnames(outdf[j]),sep="-")
      temp2 <- cor(outdf[i],outdf[j], method="pearson")
      tempV = rbind(tempV,c(temp1,temp2))
      # Create scatters using the combinations of vectors in outdf
      scatter_plot <- ggplot(outdf, aes(x=outdf[[i]],y=outdf[[j]]))
      scatter_plot <- scatter_plot + geom_point()
      scatter_plot <- scatter_plot + labs(x=colnames(outdf[i]), y=colnames(outdf[j]),
                                    title = paste(temp1, temp2, sep = ": "))
      print(scatter_plot)
    }
  }
}
```

